---
title: "PCA"
author: "massaine"
date: "2022-11-25"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE)
memory.limit(70000)
```


## Packages
```{r}
options(stringsAsFactors=FALSE)
library(prospectr)
library(caret)
library(mlbench)
library(pROC)
library(C50)
library(plsRglm)
library(stringr)
library("ROCR")
library(gt)
Cooking_traits <- c("Cook15","Cook20","Cook25","Cook30","Cook40")
```

###load data
```{r}
NIR <- "ASD"
load(file=here::here("output","dadosASD_Mas_PT.RData"))
```

### test using PLS model
```{r}
ctrl <- trainControl(method="repeatedcv",repeats = 5,
                     summaryFunction=twoClassSummary, 
                     classProbs=T, savePredictions = T,
                     verboseIter = FALSE,returnResamp = "all") 
```

### PT using PLS model to test pre treatment methods
### Cook15min
```{r}
trait <- Cooking_traits[1]
modelFit2 <- list()

for (j in 1:9) {
  dados <- dados2[[j]]
  set.seed(1)
  index <- createDataPartition(dados[,trait], p = .75, list = FALSE)
  training <- dados[index, ]
  OvSam <- subset(training,training[,trait]=="Yes")
  Ns <- round(table(training[,trait])[1]) - (nrow(OvSam)*26) 
  sample1 <- sample(x = c(1:nrow(OvSam)), size = Ns, replace = TRUE)
  x <- do.call(rbind, replicate(25, OvSam, simplify=FALSE))
  training1 <- rbind(training,x, OvSam[sample1,] )# ,OvSam[sample1,])
  table(training1$Cook15)
  training2 <- cbind(training1[,trait],training1[,c(13:ncol(training1))])
  colnames(training2)[1] <- trait
  set.seed(2304)
  modelFit1 <- train(Cook15 ~ ., data = training2, 
                          method = "pls", trControl = ctrl, 
                          preProcess = c("center","scale"),tuneLength=10)

modelFit2[[j]] <- modelFit1}
```

### results
```{r}
res <- resamples(modelFit2)
res <- res$values
resCV_1 <- list()

for(i in 1:9){
  resCV_1[[i]] <- res[,c(paste(paste("Model",i,sep = ""),"~ROC",sep = ""),
                         paste(paste("Model",i,sep = ""),"~Sens",sep = ""),
                         paste(paste("Model",i,sep = ""),"~Spec",sep = ""))]
  colnames(resCV_1[[i]]) <- c("ROC","Sens","Spec")}

resCV_2 <- do.call(rbind,resCV_1)
resCV_2$PT <- rep(c(1:9),each=50)
resCV_2$PT <- as.factor(paste("pt",resCV_2$PT,sep = "_"))
levels(resCV_2$PT) <- c("raw data", "1st","DT","MSC","SNV","1st + DT",
                        "1st + MSC","DT + MSC", "1st + SG + DT")
```

### plot Cook15
```{r}
PT_Cook15 <- resCV_2
ROC <- ggplot(PT_Cook15, aes(x=PT, y=ROC, fill=PT)) + 
  geom_boxplot()   + theme_bw() + ylim(0.82, 1) + ggtitle("ASD - Cook15")
 
Sens <- ggplot(PT_Cook15, aes(x=PT, y=Sens, fill=PT)) + 
  geom_boxplot() + theme_bw() + ylim(0.7, 1) + ggtitle("ASD - Cook15")

Spec <- ggplot(PT_Cook15, aes(x=PT, y=Spec, fill=PT)) + 
  geom_boxplot()  + theme_bw() + ylim(0.7, 1) + ggtitle("ASD - Cook15") 

```


### PT using PLS model to test pre treatment methods
### Cook20min
```{r}
trait <- Cooking_traits[2]
modelFit2 <- list()

for (j in 1:9) {
  dados <- dados2[[j]]
  set.seed(1)
  index <- createDataPartition(dados[,trait], p = .75, list = FALSE)
  training <- dados[index, ]
  OvSam <- subset(training,training[,trait]=="Yes")
  Ns <- round(table(training[,trait])[1]) - (nrow(OvSam)*9) 
  sample1 <- sample(x = c(1:nrow(OvSam)), size = Ns, replace = TRUE)
  x <- do.call(rbind, replicate(8, OvSam, simplify=FALSE))
  training1 <- rbind(training,x, OvSam[sample1,] )# ,OvSam[sample1,])
  table(training1$Cook20)
  training2 <- cbind(training1[,trait],training1[,c(13:ncol(training1))])
  colnames(training2)[1] <- trait
  set.seed(2304)
  modelFit1 <- train(Cook20 ~ ., data = training2, 
                          method = "pls", trControl = ctrl, 
                          preProcess = c("center","scale"),tuneLength=10)
  modelFit2[[j]] <- modelFit1
}

```

### results
```{r}
res <- resamples(modelFit2)
res <- res$values
resCV_1 <- list()

for(i in 1:9){
  resCV_1[[i]] <- res[,c(paste(paste("Model",i,sep = ""),"~ROC",sep = ""),
                         paste(paste("Model",i,sep = ""),"~Sens",sep = ""),
                         paste(paste("Model",i,sep = ""),"~Spec",sep = ""))]
  colnames(resCV_1[[i]]) <- c("ROC","Sens","Spec")}

resCV_2 <- do.call(rbind,resCV_1)
resCV_2$PT <- rep(c(1:9),each=50)
resCV_2$PT <- as.factor(paste("pt",resCV_2$PT,sep = "_"))
levels(resCV_2$PT) <- c("raw data", "1st","DT","MSC","SNV","1st + DT",
                        "1st + MSC","DT + MSC", "1st + SG + DT")
```

### plot Cook20
```{r}
PT_Cook20 <- resCV_2
ROC <- ggplot(PT_Cook20, aes(x=PT, y=ROC, fill=PT)) + 
  geom_boxplot()   + theme_bw() + ylim(0.8, 1) + ggtitle("ASD - Cook20")
 
Sens <- ggplot(PT_Cook20, aes(x=PT, y=Sens, fill=PT)) + 
  geom_boxplot() + theme_bw() + ylim(0.7, 1) + ggtitle("ASD - Cook20")

Spec <- ggplot(PT_Cook20, aes(x=PT, y=Spec, fill=PT)) + 
  geom_boxplot()  + theme_bw() + ylim(0.7, 1) + ggtitle("ASD - Cook20") 

```

### PT using PLS model to test pre treatment methods
### Cook25min
```{r}
trait <- Cooking_traits[3]
modelFit2 <- list()

for (j in 1:9) {
  dados <- dados2[[j]]
  set.seed(1)
  index <- createDataPartition(dados[,trait], p = .75, list = FALSE)
  training <- dados[index, ]
  OvSam <- subset(training,training[,trait]=="Yes")
  Ns <- round(table(training[,trait])[1]) - (nrow(OvSam)*4) 
  sample1 <- sample(x = c(1:nrow(OvSam)), size = Ns, replace = TRUE)
  x <- do.call(rbind, replicate(3, OvSam, simplify=FALSE))
  training1 <- rbind(training,x, OvSam[sample1,] )# ,OvSam[sample1,])
  table(training1$Cook25)
  training2 <- cbind(training1[,trait],training1[,c(13:ncol(training1))])
  colnames(training2)[1] <- trait
  set.seed(2304)
  modelFit1 <- train(Cook25 ~ ., data = training2, 
                          method = "pls", trControl = ctrl, 
                          preProcess = c("center","scale"),tuneLength=10)

modelFit2[[j]] <- modelFit1
}

```

### results
```{r}
res <- resamples(modelFit2)
res <- res$values
resCV_1 <- list()
for(i in 1:9){
  resCV_1[[i]] <- res[,c(paste(paste("Model",i,sep = ""),"~ROC",sep = ""),
                         paste(paste("Model",i,sep = ""),"~Sens",sep = ""),
                         paste(paste("Model",i,sep = ""),"~Spec",sep = ""))]
  colnames(resCV_1[[i]]) <- c("ROC","Sens","Spec")}

resCV_2 <- do.call(rbind,resCV_1)
resCV_2$PT <- rep(c(1:9),each=50)
resCV_2$PT <- as.factor(paste("pt",resCV_2$PT,sep = "_"))
levels(resCV_2$PT) <- c("raw data", "1st","DT","MSC","SNV","1st + DT",
                        "1st + MSC","DT + MSC", "1st + SG + DT")
```

### plot Cook25
```{r}
PT_Cook25 <- resCV_2
ROC <- ggplot(PT_Cook25, aes(x=PT, y=ROC, fill=PT)) + 
  geom_boxplot()   + theme_bw() + ylim(0.8, 1) + ggtitle("ASD - Cook25")
 
Sens <- ggplot(PT_Cook25, aes(x=PT, y=Sens, fill=PT)) + 
  geom_boxplot() + theme_bw() + ylim(0.7, 1) + ggtitle("ASD - Cook25")

Spec <- ggplot(PT_Cook25, aes(x=PT, y=Spec, fill=PT)) + 
  geom_boxplot()  + theme_bw() + ylim(0.7, 1) + ggtitle("ASD - Cook25") 

```



### PT using PLS model to test pre treatment methods
### Cook30min
```{r}
trait <- Cooking_traits[4]
modelFit2 <- list()

for (j in 1:9) {
  dados <- dados2[[j]]
  set.seed(1)
  index <- createDataPartition(dados[,trait], p = .75, list = FALSE)
  training <- dados[index, ]
  OvSam <- subset(training,training[,trait]=="Yes")
  Ns <- round(table(training[,trait])[1]) - (nrow(OvSam)*3) 
  sample1 <- sample(x = c(1:nrow(OvSam)), size = Ns, replace = TRUE)
  x <- do.call(rbind, replicate(2, OvSam, simplify=FALSE))
  training1 <- rbind(training,x, OvSam[sample1,] )# ,OvSam[sample1,])
  table(training1$Cook30)
  training2 <- cbind(training1[,trait],training1[,c(13:ncol(training1))])
  colnames(training2)[1] <- trait
  set.seed(2304)
  modelFit1 <- train(Cook30 ~ ., data = training2, 
                          method = "pls", trControl = ctrl, 
                          preProcess = c("center","scale"),tuneLength=10)

modelFit2[[j]] <- modelFit1
}

```

### results
```{r}
res <- resamples(modelFit2)
res <- res$values
resCV_1 <- list()
for(i in 1:9){
  resCV_1[[i]] <- res[,c(paste(paste("Model",i,sep = ""),"~ROC",sep = ""),
                         paste(paste("Model",i,sep = ""),"~Sens",sep = ""),
                         paste(paste("Model",i,sep = ""),"~Spec",sep = ""))]
  colnames(resCV_1[[i]]) <- c("ROC","Sens","Spec")}

resCV_2 <- do.call(rbind,resCV_1)
resCV_2$PT <- rep(c(1:9),each=50)
resCV_2$PT <- as.factor(paste("pt",resCV_2$PT,sep = "_"))
levels(resCV_2$PT) <- c("raw data", "1st","DT","MSC","SNV","1st + DT",
                        "1st + MSC","DT + MSC", "1st + SG + DT")
```

### plot Cook30
```{r}
PT_Cook30 <- resCV_2
ROC <- ggplot(PT_Cook30, aes(x=PT, y=ROC, fill=PT)) + 
  geom_boxplot()   + theme_bw() + ylim(0.8, 1) + ggtitle("ASD - Cook30")
 
Sens <- ggplot(PT_Cook30, aes(x=PT, y=Sens, fill=PT)) + 
  geom_boxplot() + theme_bw() + ylim(0.7, 1) + ggtitle("ASD - Cook30")

Spec <- ggplot(PT_Cook30, aes(x=PT, y=Spec, fill=PT)) + 
  geom_boxplot()  + theme_bw() + ylim(0.7, 1) + ggtitle("ASD - Cook30") 

```


### PT using PLS model to test pre treatment methods
### Cook25min
```{r}
trait <- Cooking_traits[3]
modelFit2 <- list()

for (j in 1:9) {
  dados <- dados2[[j]]
  set.seed(1)
  index <- createDataPartition(dados[,trait], p = .75, list = FALSE)
  training <- dados[index, ]
  OvSam <- subset(training,training[,trait]=="Yes")
  Ns <- round(table(training[,trait])[1]) - (nrow(OvSam)*4) 
  sample1 <- sample(x = c(1:nrow(OvSam)), size = Ns, replace = TRUE)
  x <- do.call(rbind, replicate(3, OvSam, simplify=FALSE))
  training1 <- rbind(training,x, OvSam[sample1,] )# ,OvSam[sample1,])
  table(training1$Cook25)
  training2 <- cbind(training1[,trait],training1[,c(13:ncol(training1))])
  colnames(training2)[1] <- trait
  set.seed(2304)
  modelFit1 <- train(Cook25 ~ ., data = training2, 
                          method = "pls", trControl = ctrl, 
                          preProcess = c("center","scale"),tuneLength=10)

modelFit2[[j]] <- modelFit1
}

```

### results
```{r}
res <- resamples(modelFit2)
res <- res$values
resCV_1 <- list()
for(i in 1:9){
  resCV_1[[i]] <- res[,c(paste(paste("Model",i,sep = ""),"~ROC",sep = ""),
                         paste(paste("Model",i,sep = ""),"~Sens",sep = ""),
                         paste(paste("Model",i,sep = ""),"~Spec",sep = ""))]
  colnames(resCV_1[[i]]) <- c("ROC","Sens","Spec")}

resCV_2 <- do.call(rbind,resCV_1)
resCV_2$PT <- rep(c(1:9),each=50)
resCV_2$PT <- as.factor(paste("pt",resCV_2$PT,sep = "_"))
levels(resCV_2$PT) <- c("raw data", "1st","DT","MSC","SNV","1st + DT",
                        "1st + MSC","DT + MSC", "1st + SG + DT")
```

### plot Cook25
```{r}
PT_Cook25 <- resCV_2
ROC <- ggplot(PT_Cook25, aes(x=PT, y=ROC, fill=PT)) + 
  geom_boxplot()   + theme_bw() + ylim(0.8, 1) + ggtitle("ASD - Cook25")
 
Sens <- ggplot(PT_Cook25, aes(x=PT, y=Sens, fill=PT)) + 
  geom_boxplot() + theme_bw() + ylim(0.7, 1) + ggtitle("ASD - Cook25")

Spec <- ggplot(PT_Cook25, aes(x=PT, y=Spec, fill=PT)) + 
  geom_boxplot()  + theme_bw() + ylim(0.7, 1) + ggtitle("ASD - Cook25") 

```
